A Regularized Time Varying Vector Error Correction Model

### 2017-03-31 articles-conferences/elsevier-2016/src/background.tex
adding comment characters in crossvalidation section

%'---------------------------http://robjhyndman.com/hyndsight/crossvalidation/
When the data are not independent cross-validation becomes more difficult as leaving out an observation does not remove all the associated information due to the correlations with other observations. For time series forecasting, a cross-validation statistic is obtained as follows

Fit the model to the data y1,…,yt and let y^t+1 denote the forecast of the next observation. Then compute the error (et+1∗=yt+1−y^t+1) for the forecast observation.
Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
Compute the MSE from em+1∗,…,en∗.
References

An excellent and comprehensive recent survey of cross-validation results is Arlot and Celisse (2010)

>>>>

%'---------------------------http://robjhyndman.com/hyndsight/crossvalidation/
%When the data are not independent cross-validation becomes more difficult as leaving out an observation does not remove all the associated information due to the correlations with other observations. For time series forecasting, a cross-validation statistic is obtained as follows

%Fit the model to the data y1,…,yt and let y^t+1 denote the forecast of the next observation. Then compute the error (et+1∗=yt+1−y^t+1) for the forecast observation.
%Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
%Compute the MSE from em+1∗,…,en∗.
%References

%An excellent and comprehensive recent survey of cross-validation results is Arlot and Celisse (2010)
